% !TEX root = ../main.tex
\chapter{Conclusion}\label{ch:chapter6} % For referencing the chapter elsewhere, use \ref{Chapter1}
%
%%----------------------------------------------------------------------------------------
%
In this dissertation we have presented a fast
intra mode decision algorithm for depth maps to
address the time cost issue of depth map coding, leveraging 
the learned models, which are constructed from deep
convolutional neural networks, to predict the wedgelet angles
for the CUs in the depth maps.
The predictions from the learned models are capable of
reducing the number of intra candidates by half for both
conventional intra angular modes and DMM1 wedgelets in depth map coding.
The size of the neural network has been carefully designed to balance
the trade-off between the time cost of model prediction and the model prediction
accuracy.
Confusion matrix is at the core of the stopping criteria.
Top-k criteria is utilized to perform the prediction.
The learned models are integrated into the reference software of
3D-HEVC for the simulations.
The compiled executable binaries are able to harness
the power of the simultaneous computation of CPU, as well as
the parallel computation of GPU to accelerate the 
predictions.
The simulation results show that the proposed algorithm
provides 64.6\% time reduction in average 
for DMM1 wedgelet searching
in depth maps while the
BD performance has a trivial decrease comparing 
with the most recent implementation of 3D-HEVC
standard.
